%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Licence:
% CC BY 3.0 (http://creativecommons.org/licenses/by/3.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, oneside, final, 11pt]{scrartcl} % Paper options using the scrartcl class


%----------------------------------------------------------------------------------------
%	PACKAGEz
%----------------------------------------------------------------------------------------
\usepackage[hmargin=1.75cm,vmargin=1.75cm]{geometry} % Options including margin size
\usepackage[T1]{fontenc} % Fonts
\usepackage[utf8]{inputenc} % Fonts
\usepackage{titlesec} % Allows creating custom \section's
\usepackage{helvet} % Import font
\usepackage{nopageno} % Suppress page numbers
\usepackage{fontawesome} % Icons
\usepackage{hyperref} % So URLs don't fall off the page



%----------------------------------------------------------------------------------------
%	SET UP DOCUMENTnnn
%----------------------------------------------------------------------------------------

% Base fonts
\renewcommand*{\ttdefault}{lmvtt}

% Section and subsection headings
\titleformat{\section}{}{}{0em}{}[\titlerule]
\titleformat*{\section}{\fontfamily{phv}\bfseries\scshape\fontsize{16pt}{16pt}\selectfont} 
\titlespacing\section{0pt}{20pt plus 4pt minus 2pt}{14pt plus 2pt minus 2pt}
\titleformat*{\subsection}{\fontfamily{phv}\bfseries\scshape\fontsize{13pt}{13pt}\selectfont} 
\titlespacing\subsection{0pt}{16pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}
\titleformat*{\subsubsection}{\fontfamily{phv}\bfseries\scshape\fontsize{11pt}{11pt}\selectfont} 
\titlespacing\subsubsection{0pt}{5pt plus 2pt minus 1pt}{4pt plus 1pt minus 1pt}

% Paragraphs
\setlength{\parindent}{0cm}

% URLs
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% HEADER SECTION
%----------------------------------------------------------------------------------------


%\makebox[1\textwidth]
{\fontfamily{phv}\fontsize{21}{21}\bfseries\scshape{Robbie Waller, MEng\,(Hons) PGDip}} % Name at the top

\bigskip

\faEnvelopeO \space rob@robbiewaller.co.uk \hfill  \faMobile \space +44 7523 207689

\smallskip

%----------------------------------------------------------------------------------------
%	PERSONAL STATEMENT
%----------------------------------------------------------------------------------------
\section{Personal Statement}

I am an experienced and enthusiastic Nuclear Engineer, specialising in assurance and management of nuclear operations. I have six years of unique experience operating and managing naval nuclear reactors in the USA and the UK. I now intend to apply my knowledge to assurance activities in the UK nuclear power sector. Operating as an individual and leading teams, I have a proven track record in being highly adaptable across multiple areas of the nuclear enterprise, with excellent problem solving skills. This broad base drives my strong interest in an assurance role. I maintain a questioning attitude to the status-quo, underpinned by a strong sense of moral courage and backed up by absolute professionalism. 


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\subsubsection*{Engineering Charge Qualification,\textnormal{ Naval Reactors, Washington DC} \hfill 2018} 
\subsubsection*{Postgraduate Diploma, \textnormal{Nuclear Reactor Technology, Cranfield University} \hfill 2013}  
\subsubsection*{MEng (Hons), \textnormal{Mechanical Engineering, University of Southampton} \hfill 2011} 


%\begin{itemize}
%\item Engineering Charge Qualification, Naval Reactors, Washington DC \hfill 2018
%\item Postgraduate Diploma, Cranfield University, Nuclear Reactor Technology \hfill 2013
%\item MEng (Hons), Mechanical Engineering, University of Southampton \hfill 2011
%\end{itemize}




%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

\subsubsection*{Submarine Assurance Officer, Navy Command \hfill 2018--2020}  
\normalfont
\begin{itemize}

\item Responsible for providing
assurance that the Submarine Service operated within its Nuclear Authorisation Conditions as well as the health, safety and environmental constraints of the Defence Maritime Regulator (DMR).

\item Acted as the focal point for regulator interaction. Conducted independent third party nuclear assurance audits across the organisation. Identified, managed and corrected nuclear non-compliance findings as well as DMR findings. Identified major non-compliance issue against unauthorised changes to the nuclear-baseline, demonstrating moral courage to highlight and pursue the issue. 

\item Analysed data from Organisational Learning reports to identify adverse trends in safety culture. Communicated and implemented lessons learnt to prevent reoccurrence. Conducted analysis on refrigerant gas loss data, highlighting adverse trend in shut-down plant gas retention. 

\end{itemize}

\smallskip 

\subsubsection*{Safety Delivery Manager,  Nuclear Propulsion Project Team, MOD \hfill 2018--2019}  
\normalfont
\begin{itemize}

\item Acted as project lead for a nuclear engineering safety case development programme.  Responsible for interpreting experimental and calculated data to provide recommendations on safety case limitations for future operation.

\item Responsible for data analysis of studies conducted by the Technical Authority (Rolls Royce) and the Independent Nuclear Authority (Wood Group). Made recommendations to the Defence Nuclear Safety Regulator that plants were safe to operate,  subsequently extending the operational life of two nuclear plants.

\item Acted as an Assistant Duly Authorised Person (ADAP). 

\end{itemize}


				
\subsubsection*{Electrical Officer \& Assistant Engineer \hfill 2016--2018}  
\normalfont
\begin{itemize}

	 
	\item 2000 hours experience as Qualified Critical plant supervisor and 50 days of experience as Shutdown plant supervisor. Successfully led and co-ordinated six reactor startups and shutdowns.
	
\item  Responsible for \$1.5 billion submarine alongside, managing a team of 25 technical specialists for 24-hour periods. Duties included supervising all routine maintenance activities, correcting emergent defects, and managing the Safe System of Work and emergency response, including leading the onboard response to a nuclear emergency.  
\item Responsible for Audit and Surveillance programme. As an inspector, monitoring conduct of routine plant maintenance and operations to ensure compliance with procedures, work practices and SSHE arrangements. 

\item Passed 15 hours of professional examinations and interviews at Naval Reactors in Washington DC (PNEO), giving certification to operate as the Senior Supervisor on a US Navy nuclear plant. 

\item Qualified as a Duly Authorised Person (DAP), providing oversight to complex nuclear operations including cool downs, control rod testing, switchboard maintenance and live plant drill periods.
\end{itemize}



\subsubsection*{Submarine Sustainable Manning Programme \hfill 2015--2016}  
\normalfont
\begin{itemize}
	\item Co-ordinated a study with independent consultants, analysing novel methods of staffing nuclear control rooms with contractors during maintenance periods. Conducted detailed analysis of a shut-down nuclear operator to build a required set of competencies to allow for contractorisation.
	
	\item  Resulted in two contractors undertaking trial periods of nuclear operation on a submarine. Collected data and feedback from study to provide recommendations for future work. \end{itemize}


				
\subsubsection*{Naval Nuclear Power Training Command \hfill 2014--2015}  
\normalfont
\begin{itemize}
	\item Selected by senior management as top student of 18 candidates on an engineering graduate scheme to undertake a prestigious three-year exchange with the US Navy. 
	
	\item Undertook six months of rigorous academic training and a further six month period of practical training on a critical prototype S5W reactor at Naval Nuclear Power Training Unit Charleston.
	\item Certified by the US Navy and the US Department of Energy to act as Nuclear Engineering Officer of the Watch, qualifying early, with above average marks in all assessments.
\end{itemize}


				
\subsubsection*{Assistant Marine Engineering Officer (Training) \hfill 2012--2014}  
\normalfont
\begin{itemize}
	\item Selected for a two year Royal Navy graduate scheme, comprising theoretical and practical training in mechanical systems, electronics, refrigeration, nuclear theory, reactor design, nuclear health physics and nuclear systems. Passed course with Distinction and an award for the best research project. 
	\item Qualified as a nuclear engineering spaces watch-keeper and a nuclear electrical panel operator. 
	\item Conducted  three month period of independent research into a tritium monitoring facility in a radio-chemistry lab. Designed, ran and evaluated experiments using a Liquid Scintillation Counter (LSC) resulting in the development of Standard Operating Procedures and commissioning for future testing. 
	\item Conducted a technical review of state-of-the-art LSC techniques for solid sampling, the output of which was a presentation to an industry partner on methods for optimising their `tritium analysis in solids' techniques.
\end{itemize}




%----------------------------------------------------------------------------------------
%	FURTHER INFORMATION
%----------------------------------------------------------------------------------------
\section{Further Information}
\subsubsection*{Professional Memberships}

\begin{itemize}	
\item Chartered Engineer, Institute of Mechanical Engineering (submitted, awaiting interview).
\item Security-cleared to a high government standard.
\end{itemize}


\subsubsection*{Langauges}
\begin{itemize}	
\item Fluency in technical and conversational French. 2011: six months of engineering study at the French Naval Academy as part of an exchange programme. 
\item Conversational German. 
\end{itemize}



\subsubsection*{Interests}
\begin{itemize}	
 \item RYA Yachtmaster Instructor.
 \item Motorcycles. 
\end{itemize}






%----------------------------------------------------------------------------------------
%	APPENDIX
%----------------------------------------------------------------------------------------

\end{document}